Error propagation error

### 2022-01-10 doc/method_validation/method_validation.Rmd
Update for amsdata

```{r}
library(tidyverse)
library(hgis)
library(readxl)
library(here)
library(errors)
library(janitor)
```

@@

dfe <- df %>% 
  mutate(corr_14_12_err = set_errors(corr_14_12, max_err),
         norm_ratio_err = norm_gas(corr_14_12_err, ratio_std, fm_std))

>>>>

```{r}
library(tidyverse)
library(hgis)
library(readxl)
library(here)
library(errors)
library(janitor)
library(amsdata)
```

@@

dfe <- df %>% 
  mutate(corr_14_12_err = set_errors(corr_14_12, max_err),
         norm_ratio_err = norm_run(corr_14_12_err, ratio_std, fm_std))
